\thesistitle

### 2019-06-12 sections/research.tex
Type 3R Clones

$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}$$
$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
$$l=Number\ of\ literals$$
$$v=Number\ of\ variables$$
$$m=Number\ of\ method\ calls$$
$$t=Number\ of\ tokens$$

@@

\section{Type 3R clones}
Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements. For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself. The main question for this study regarding type 3 clones is: \textit{``how can we refactor type 3 clones while improving the design?''}.

Clone instances in type 3 clones are almost always different in functionality. As we have to ensure equal functionality after refactoring the clone, we have to wrap the difference in statements between the clone instances in conditional blocks. We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration). Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.

We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account). As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection. By trying to find short gaps between clones, we can find opportunities to refactor clone classes into a single type 3 clone class. The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.

@@

Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects. Because of this, these definitions may be less suitable for large scale clone detection purposes.

>>>>

$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
$$l=Number\ of\ literals$$
$$v=Number\ of\ variables$$
$$m=Number\ of\ method\ calls$$
$$t=Number\ of\ tokens$$

@@

\section{Type 3R clones}
Type 3 clones allow any change in statements, often bounded by a similarity threshold. This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. See figure \ref{fig:type3} for an example of such a clone.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/type3_3}
  \caption{Added statement between cloned methods.}
  \label{fig:type3}
\end{figure}

In figure \ref{fig:type3} a single statement is added. This statement is found in between cloned lines. We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}. This gap has a threshold for type 3R, which is calculated by the following formula:

$$T3R\ Gap\ Percentage=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = The\ amount\ of\ statements\ in\ this\ code\ fragment$$
$$C_{gap} = The\ gap between two clones$$
$$C_{above} = The\ clone\ instance\ above\ the\ gap$$
$$lower = The clone instance below the gap$$

Apart from this threshold, the gap in between clones may not span over different blocks. Look at figure \ref{fig:type3invalid} for an example of this. We cannot refactor both statements into a single conditional block. We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{img/type3invalid}
  \caption{Statements between clones in different blocks.}
  \label{fig:type3invalid}
\end{figure}

@@

Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects. Because of this, the proposed clone definitions may be less suitable for large scale clone detection purposes.
